\section{Phrasal verbs and expressions}
\begin{multicols}{2}
\begin{description}
\item [Bring up]. Talk about something.
\begin{itemize}
\item I'll \textcolor{blue}{bring up} my concerns for the meeting.
\item If you \textcolor{blue}{bring} your dubts \textcolor{blue}{up}, we can solve them.
\item He \textcolor{blue}{brought} it \textcolor{blue}{up} again when we were talking about other topic.
\item She'd \textcolor{blue}{brought} it \textcolor{blue}{up} to clarify ideas.
\item We'd \textcolor{blue}{brought} our difficulties \textcolor{blue}{up} in the meeting with our friends.
\item They've \textcolor{blue}{bring up} the project requirements to the meeting with the client.
\end{itemize}

\item[Catch it] hear it.
\begin{itemize}
\item I've \textcolor{blue}{caught it} despite the environmental noise.
\item You \textcolor{blue}{catch it} everything they said, didn't you?.
\item He would \textcolor{blue}{catch it} clearly.
\item Did she \textcolor{blue}{catch it}?
\item We didn't \textcolor{blue}{catch it}, could you repeat, please?
\item They \textcolor{blue}{catch it} all the instructions.
\end{itemize}
\item [Crop up] \emph{(Surgir)}.
\begin{itemize}
\item I \textcolor{blue}{crop up} when you wish. (The genius)
\item You \textcolor{blue}{cropped up} constantly when we're in troubles. (To Spider-man)
\item He's been \textcolor{blue}{cropping up} during the courses.
\item She'll \textcolor{blue}{crop up} soon because of the loud music.
\item We'll not \textcolor{blue}{crop up} by there, we're sorry.
\item They've been \textcolor{blue}{cropping up} regularly.
\end{itemize}

\item [Get along =] to meet and enjoy
\begin{itemize}	
\item I \textcolor{blue}{got along} with my friends last night.
\item Do You \textcolor{blue}{get along} here with he?
\item He \textcolor{blue}{gets along} with she skating.
\item She \textcolor{blue}{got along} with her team yesterday.
\item We will \textcolor{blue}{get along} playing soccer.
\item They'd \textcolor{blue}{get along} if they keep calm.
\end{itemize}
\item [Get going]. Need to leave.
\begin{itemize}
\item I have to \textcolor{blue}{get going} because I have an appointment with my doctor.
\item You had to \textcolor{blue}{get going} to avoid be late.
\item He'll \textcolor{blue}{get going} after the meeting.
\item Has she \textcolor{blue}{get going}?
\item Will we \textcolor{blue}{get going}?
\item Had they \textcolor{blue}{got going}?
\end{itemize}
\item[Get it] Understand it.
\begin{itemize}
\item I got it each idea you exposed.
\item You get 
\item He\dots
\item She\dots
\item We\dots
\item They\dots
\end{itemize}
\item [Get the hang of it =] If you're learning some new.
\begin{itemize}
\item I'm \textcolor{blue}{getting the hang} of the english with this course.
\item You \textcolor{blue}{get the hang} to this board game
\item He \textcolor{blue}{got the hang} of this application too quickly.
\item She'd \textcolor{blue}{got the hang} of algebra through a lot of practice.
\item We're \textcolor{blue}{getting the hang} thanks our teacher.
\item They practiced until they \textcolor{blue}{got the hang} of the tool.
\end{itemize}
\item [Get together =] to meet.
\begin{itemize}
\item I \textcolor{blue}{get together} with you tomorrow.
\item You're \textcolor{blue}{getting together} with the clients.
\item He \textcolor{blue}{gets together} with his friends.
\item She \textcolor{blue}{got together} yesterday with the students.
\item We'd \textcolor{blue}{got together} to go to the concert yesterday.
\item They've \textcolor{blue}{get together} to set up the gallery.
\end{itemize}

\item[Have got to / Have to] Need to\dots
\begin{itemize}
\item I\dots 
\item You\dots 
\item He\dots
\item She\dots
\item We\dots
\item They\dots
\end{itemize}

\item [Not always be right =] Not always to have a correct answer.
\begin{itemize}
\item \textcolor{blue}{Not always I'm right}. Sometimes I have mistakes.
\item \textcolor{blue}{Not always You're right}, are you?
\item He \textcolor{blue}{not always is right} because he is learning.
\item She \emph{always is right}, even if she \textcolor{blue}{not always is right}.
\item We \textcolor{blue}{not always are right} although we've did a lot of projects.
\item They \textcolor{blue}{not always were right}, they've had to learn a lot.
\end{itemize}

\item[Run it by] To tell about something before do it.
\begin{itemize}
\item I\dots 
\item You\dots 
\item He\dots
\item She\dots
\item We\dots
\item They\dots
\end{itemize}

\item [To show up =] To arrive; come to aplace.
\begin{itemize}
\item I \textcolor{blue}{showed up} at the party at the right moment.
\item You \textcolor{blue}{show up} in the airport just in time.
\item He \textcolor{blue}{shows up} by the college sometimes.
\item She \textcolor{blue}{showed up} here 50 minutes ago.
\item We're \textcolor{blue}{showing up} soon.
\item They \textcolor{blue}{showed up}, by the way, in the research center.
\end{itemize}
\item [To speak out =] To say what you think.
\begin{itemize}
\item I \textcolor{blue}{speak} you \textcolor{blue}{out} about this situation.
\item You can \textcolor{blue}{speak} this \textcolor{blue}{out} if it's required.
\item He \textcolor{blue}{speaks} the problem \textcolor{blue}{out} during the meeting.
\item She \textcolor{blue}{spoke out} what she though.
\item We \textcolor{blue}{spoke} a lot \textcolor{blue}{out} about the poem.
\item They're \textcolor{blue}{speaking} us \textcolor{blue}{out} what they found.
\end{itemize}

\item [Wrap up]. Finish something.
\begin{itemize}
\item I've to \textcolor{blue}{wrap up} today if I like vacation.
\item You'd \textcolor{blue}{wrapped} this \textcolor{blue}{up} recently. Good job!
\item He \textcolor{blue}{wraps up} his most difficult course.
\item She's \textcolor{blue}{wapping up} her homework.
\item We must \textcolor{blue}{wrap up} our duties quickly.
\item They're \textcolor{blue}{wraping} your order \textcolor{blue}{up} in this moment.
\end{itemize}

\item [Description] = \textcolor{blue}{Number} - \textcolor{red}{Opinion} - \textcolor{brown}{Size} - \textcolor{teal}{Age} - \textcolor{orange}{Shape} - \textcolor{purple}{Color} - \textcolor{cyan}{Nationality}.
\begin{itemize}
\item I found my \textcolor{blue}{two} \textcolor{brown}{small} \textcolor{teal}{old} \textcolor{orange}{square} \textcolor{purple}{brown} \textcolor{cyan}{chinese} seats.
\item You\dots
\item He\dots
\item She\dots
\item We\dots
\item They\dots
\end{itemize}
\end{description}
\end{multicols}