\section{Vocabulary}
\begin{multicols}{2}
\begin{description}

\item[-ache] Small to medium pain.

\item[Although] \emph{(Aunque)}
\begin{itemize}
\item \textcolor{blue}{Although} I hate too much theory, I must study sometimes a few topics.
\item You must eat everything \textcolor{blue}{although} you don't like it.
\item \textcolor{blue}{Although} he is very strong, he doesn't have to carry all the things.
\item Does she prefer that thing \textcolor{blue}{although} this is better?
\item We'll do that \textcolor{blue}{although} we don't know each aspect at this moment.
\item They became the best team \textcolor{blue}{although} at the beginning they didn't know it.
\end{itemize}

\item[Assurance]

\item[Attentive] Helpful.
\begin{itemize}
\item I like to be \textcolor{blue}{attentive}.
\item You are \textcolor{blue}{attentive}.
\item His maners means that he is very \textcolor{blue}{attentive}.
\item She is so \textcolor{blue}{attentive}, she doesn't miss anything.
\item We have to be \textcolor{blue}{attentive} to keep our quality.
\item If they're \textcolor{blue}{attentive}, they'll find the way to win.
\end{itemize}

\item[Authorize] Allows to a person or group to access.
\begin{itemize}
\item I \textcolor{blue}{authorize} your access to this area.
\item You \textcolor{blue}{authorized} the departure of the ship.
\item He can't be \textcolor{blue}{authorized} to use that equipment.
\item She'll be \textcolor{blue}{authorized} to go away on vacation.
\item We've been \textcolor{blue}{autorized} to go in and repair the failure.
\item They've not \textcolor{blue}{authorized} to pick you up this packages.
\end{itemize}

\item[Availability]

\item[Aware] Having knowledge or perception of a situation or fact.
\begin{itemize}
\item I'm well \textcolor{blue}{aware} of the problem.
\item You're \textcolor{blue}{aware} you have to study a little more.
\item He's \textcolor{blue}{aware} he need a new computer but he still doing his best.
\item She was \textcolor{blue}{aware} of your problem, keep calm.
\item We've been \textcolor{blue}{aware} of the circumstances of the project.
\item They \textcolor{blue}{aware} about the issue very well.
\end{itemize}
\item[Benefits] [\emph{\textipa{ben@fits}}] Advantages or "perks". Mostly health related things.

\item[Besides] In addition to\dots
\begin{itemize}
\item I like do early exercise everyday, \textcolor{blue}{besides}, I love it during cold season.
\item You're a great friend, \textcolor{blue}{besides}, you're a formidable leader.
\item He could help us, \textcolor{blue}{besides}, he is an expert in this area.
\item She is very good baking cakes, \textcolor{blue}{besides}, she's the chef in her own restaurant.
\item We are too many, \textcolor{blue}{besides}, we eat a lot.
\item They are good doctors, \textcolor{blue}{besides} they always are researching and improving their techniques.
\end{itemize}

\item[Cheering] Claping.

\item[Clever] A smart and witty person.

\item[Confidentiality]

\item[\emph(to) Cope] To deal effectively with something.
\begin{itemize}
\item I \textcolor{blue}{cope} with different technologies in each project.
\item You \textcolor{blue}{coped} these things very well.
\item He will \textcolor{blue}{cope} according his experience.
\item She would \textcolor{blue}{cope} those things.
\item We are cappable \textcolor{blue}{to cope} different situations.
\item They were going \textcolor{blue}{to cope} without any preparation.
\end{itemize}

\item[Courteous / Discourteous] Polite / impolite.

\item[Cozy] \emph{(Acogedor)}.

\item[Delight] Great pleasure.
\begin{itemize}
\item I'm a \textcolor{blue}{delight} (the jam).
\item You \textcolor{blue}{delight} reading these books.
\item He is \textcolor{blue}{delighting} his coffee.
\item She \textcolor{blue}{delights} traveling.
\item We \textcolor{blue}{delight} the performance at the theater.
\item They \textcolor{blue}{delighted} with my cheesecake.
\end{itemize}

\item[Delightful] Charming.
\begin{itemize}
\item I'm eating this \textcolor{blue}{delightful} cake.
\item You drink that \textcolor{blue}{delightful} tea.
\item He makes \textcolor{blue}{delightful} coffees.
\item She feels \textcolor{blue}{delightful}.
\item We think this music is \textcolor{blue}{delightful}.
\item They played a \textcolor{blue}{delightful} music during the concert.
\end{itemize}

\item[Desert] A dry region with few plants, animals or water.

\item[Dissatisfied] Not happy with something.

\item[Efficient] Well organized.

\item[Existing] present.

\item[Flexible] [\emph{\textipa{flek-s@-bul}}] Able to change or adapt.

\item[Furtheremore] \emph{(Es más)}.
\begin{itemize}
\item Everyday I do excercise, \textcolor{blue}{furthermore}, I love swimming very early, at 5:00 a. m.
\item You are an excellent student, \textcolor{blue}{furthermore}, you're in the Honor list.
\item He likes play music, \textcolor{blue}{furthermore}, he loves play piano every day.
\item She is a good chef, \textcolor{blue}{furthermore}, her cakes are the best.
\item We went to hiking yesterday, \textcolor{blue}{furthermore}, we hiked in the hills.
\item They did a good job, \textcolor{blue}{furthermore}, their project is very useful.
\end{itemize}

\item[Goods] Products to buy or sell.

\item[Havoc] \emph{(\textipa{`haev@k})} Serious damage.

\item[Health] My own health

\item[Healthcare] The system related to ensure the health of the people.

\item[High-quality] Of a very good standard.

\item[Household] \emph{(Familiar)}.

\item[However] \emph{(Sin embargo)}
\begin{itemize}
\item I have a hard time learning React, \textcolor{blue}{however}, I keep learning.
\item You woke up late, \textcolor{blue}{however}, awesomely you arrived on time.
\item He is learning play guitar, \textcolor{blue}{however}, he's very good with that.
\item She does a lot of thigns, \textcolor{blue}{however}, whe never seems to be tired.
\item We did our best, \textcolor{blue}{however}, it wasn't enoght.
\item Everything are fixed, \textcolor{blue}{however}, the Earth moves.
\item They eat a lot, \textcolor{blue}{however}, they aren't fat.
\end{itemize}

\item[Integrity] The information must be complete and fulfill some rules and characterstics, adding, pudating and deletion must match those rules.

\item[Leisure] Free time.
\begin{itemize}
\item I have no idea what to do during my \textcolor{blue}{leisure}.
\item You have a large \textcolor{blue}{leisure} time. Try to relax you.
\item He sleeps a lot in his \textcolor{blue}{leisure}.
\item She has \textcolor{blue}{leisure} and uses it to learn new things.
\item We don't waste our time, even during our \textcolor{blue}{leisure} we do things.
\item They're more creative in the \textcolor{blue}{leisure}.
\end{itemize}

\item[Loyal] Faithful and supportive.

\item[Loyalty]Dedication to something.

\item[Kingdom] A region or country with a king or queen.

\item[Manner] The way to do\dots
\begin{itemize}
\item I do the things in my own \textcolor{blue}{manner}.
\item Your \textcolor{blue}{manner} of paint is awesome.
\item He has a great \textcolor{blue}{manner} to swim.
\item She had an exceptional \textcolor{blue}{manner} to handle these things.
\item Our \textcolor{blue}{manner} to communicate could be more efficient.
\item They explain in a \textcolor{blue}{manner} that enchant.
\end{itemize}

\item[Migraine]

\item[Moreover] \emph{(Además)}
\begin{itemize}
\item I frequently do exercice very eary \textcolor{blue}{moreover} I practice a little of karate as I remembered.
\item You make beautiful handicrafts, \textcolor{blue}{moreover}, you learn new techniques frequently.
\item He everyday practices piano \textcolor{blue}{moreover} he searches a new course.
\item She is very trustworthy \textcolor{blue}{moreover} is very generous.
\item We can repair this \textcolor{blue}{moreover} we could make a beter new thing.
\end{itemize}

\item[Nevertheless] However.
\begin{itemize}
\item I studied a lot of courses \textcolor{blue}{nevertheless} I need to practice all those things.
\item You want to go out \textcolor{blue}{nevertheless} we can't do that 'cause pandemic.
\item He organized a party \textcolor{blue}{nevertheless} nobody assisted.
\item She made a painting \textcolor{blue}{nevertheless} she must makes more paintings
\item We want to play basketball \textcolor{blue}{nevertheless} we need two players more.
\item They bought some plants \textcolor{blue}{nevertheless} they forgot the vases.
\end{itemize}

\item[Options] Choices.

\item[Overwhelmed] \dots of a lot of things to do or too much troubles to solve.
\begin{itemize}
\item I feel \textcolor{blue}{overwhelmed} withall this troubles.
\item You must plan your activities to avoid \textcolor{blue}{overwhelm}.
\item He \textcolor{blue}{overwhelms} too frequent.
\item She \textcolor{blue}{overwhelms} us with a lot of requirements in a short time.
\item We've to organize our time and say ``stop'' when we must or else we'll be \textcolor{blue}{overwhelmed}.
\item They \textcolor{blue}{overwhelm} their team during this season.
\end{itemize}

\item[Pain] A serious pain.

\item[Pairwise] Organized by groups of two elements.

\item[Perks] things given to employees to keep them happy.

\item[Primary Care Physician] A doctor who treats the emergency GENERAL CASES. URGENT CARE.

\item[Radiosity] \emph{(Radiosidad)}.

\item[Regardless] \emph{(Independientemente)}
\begin{itemize}
\item I play now \textcolor{blue}{regardless} if you want.
\item \textcolor{blue}{Regardless} the difficulty, you can do it.
\item He is an exceptional athlete \textcolor{blue}{regardless} of the competition.
\item She bought those blouses \textcolor{blue}{regardless} the price.
\item We keep us in touch \textcolor{blue}{regardless} of the distance.
\item They are continuing training \textcolor{blue}{regardless} if they're tired.
\end{itemize}

\item[Reliable] [\emph{\textipa{r@'li@b(@)l}}] Trustworthy. Able to be trusted.
\begin{itemize}
\item I prefer a \textcolor{blue}{reliable} equipment
\item You made a \textcolor{blue}{reliable} engine
\item He is a \textcolor{blue}{reliable} leader
\item She prefers a \textcolor{blue}{reliable} source of money instead of risky incomings.
\item We are a \textcolor{blue}{reliable} team.
\item They found a \textcolor{blue}{reliable} source of resources.	
\end{itemize}

\item[Resilient] Able to withstand or recover quickly from difficult conditions.
\begin{itemize}
\item I'm not very \textcolor{blue}{resilient} sometimes in my job.
\item If you're \textcolor{blue}{resilient}, you'll avoid to be overwhelmed.
\item He must be \textcolor{blue}{resilient} if he wants to keep his job.
\item She's looking for a \textcolor{blue}{resilient} employee.
\item We affront too many changes, so we must be \textcolor{blue}{resilient}.
\item They became \textcolor{blue}{resilient} after many years of work.
\end{itemize}

\item[Repeat] Returning.

\item[Responsive] Reacting quickly and positive.

\item[Route] A specific path from one place to another place

\item[Satisfied] Happy with something.

\item[Security system] A system that assures the security of the information (integrity, availability, confidentiality).

\item[Skim] \emph{(Desnatar)}.

\item[Staff morale] Work climate.

\item[Stop] A place to rest during a long trip.

\item[Struggle] to make an effort to do something.
\begin{itemize}
\item I \textcolor{blue}{struggle} to keep calm everyday.
\item You must \textcolor{blue}{struggle} if you want to rise.
\item He \textcolor{blue}{struggled} too hard to become the boss.
\item She is \textcolor{blue}{struggling} against the difficulties.
\item We have to \textcolor{blue}{struggle} if we want to win.
\item They must \textcolor{blue}{struggle} to get the prize.
\end{itemize}

\item[Sub-standard] Not as good as normal.

\item[Therefore] Consequently, So, 
\begin{itemize}
\item I studied Computer Sciences, \textcolor{blue}{therefore} I'd must love maths.
\item You make very beautiful drawings, \textcolor{blue}{therefore} you're very skilled with that.
\item He has a meeting, \textcolor{blue}{therefore} he's getting going.
\item She's very organized, \textcolor{blue}{therefore} she has everything ready.
\item We'll affront too many changes, \textcolor{blue}{therefore} we must be resilient.
\item They forgot the keys, \textcolor{blue}{therefore} they must come back soon.
\end{itemize}

\item[Through] \emph{(A través de)}
\begin{itemize}
\item I saw the stars \textcolor{blue}{through} my telescope.
\item You walked \textcolor{blue}{through} the bridge.
\item He sang very loud \textcolor{blue}{through} the mic.
\item Awesomely she wrapped up her project \textcolor{blue}{through} a so difficult path.
\item We hiked \textcolor{blue}{through} beautiful paths.
\item They arrived \textcolor{blue}{through} the most difficult route.
\end{itemize}

\item[Thus] Then, Hence, Therefore.

\item[Trade] Buying or selling something.

\item[Uncaring] Not sympathetic.

\item[Upon] \emph{(Sobre)}.
\begin{itemize}
\item I wore the jacket \textcolor{blue}{upon} my sweater.
\item You drew \textcolor{blue}{upon} your previous sketch.
\item He put a barrier \textcolor{blue}{upon} himself.
\item She jumped \textcolor{blue}{upon} the wall.
\item We put the decoration \textcolor{blue}{upon} the fence.
\item They painted \textcolor{blue}{upon} the graffiti.
\end{itemize}

\item[Whatever] \emph{(Lo que sea)}
\begin{itemize}
\item I eat almost \textcolor{blue}{whatever} that contains meat.
\item You're capable to do \textcolor{blue}{whatever} in this department.
\item He can work in \textcolor{blue}{whatever} he want.
\item she says that she likes write about \textcolor{blue}{whatever}.
\item We play \textcolor{blue}{whatever} with the ball.
\item \textcolor{blue}{Whatever} they choice is the correct option.
\end{itemize}

\item[Whenever] \emph{(Cuando sea)}
\begin{itemize}
\item I'll always be here for you \textcolor{blue}{whenever} you need.
\item You must be ready for the test \textcolor{blue}{whenever} it will be.
\item He is available \textcolor{blue}{whenever} we require him.
\item \textcolor{blue}{Whenever} she wants we're ready.
\item we depart \textcolor{blue}{whenever} the ship arrives.
\item They write their ideas \textcolor{blue}{whenever} because they always carry notebooks.
\end{itemize}

\item[Whereas] \emph{(Mientras que)}.
\begin{itemize}
\item \textcolor{blue}{Whereas} I balance the act, the requirements become more urgents.
\item You study in the morning \textcolor{blue}{whereas} you play in the afternoon.
\item He can do beautiful paintings \textcolor{blue}{whereas} he suffers cooking.
\item She loves chocolate \textcolor{blue}{whereas} she is allergic to seafood.
\item We breakfast \textcolor{blue}{whereas} you slept.
\item They were arriving \textcolor{blue}{whereas} we were leaving.
\end{itemize}

\item[Wherever] \emph{(Donde sea)}
\begin{itemize}
\item I can work almost \textcolor{blue}{wherever}.
\item You're lucky because you can train \textcolor{blue}{wherever} you want.
\item He always wins \textcolor{blue}{wherever} he plays.
\item \textcolor{blue}{Wherever} she  works, everything seems organized.
\item We can travel \textcolor{blue}{wherever}.
\item They paint \textcolor{blue}{wherever} they're required.
\end{itemize}

\item[Witty] Showing or characterized by quick and inventive verbal humor.
\begin{itemize}
\item I think I have a \textcolor{blue}{witty} humor sense.
\item You're a \textcolor{blue}{witty} wise person.
\item He makes very \textcolor{blue}{witty} jokes quickly.
\item She writes \textcolor{blue}{witty} comics.
\item We think the comedian is too \textcolor{blue}{witty}.
\item They perform a \textcolor{blue}{witty} circus act.
\end{itemize}

\item[Work climate] The attitude, satisfaction and overall outlook of employees at the work place.

\item[Work remotely]To work from home, outside of the office.

\item[Workoholic] A person who works a lot.

\item[Wreak] \emph{(\textipa{Rik})} To cause, To inflict.
\begin{itemize}
\item I \textcolor{blue}{wreak} serious harm to his forces.
\item You \textcolor{blue}{wreaked} pain to them
\item He \textcolor{blue}{wreaks} havoc to other players.
\item She'd seriusly \textcolor{blue}{wreaks} harm to his army. (Risk board game)
\item We \textcolor{blue}{wreak} great havoc to the planet.
\item They alert us of \textcolor{blue}{wreaking} damage to the zone.
\end{itemize}
\end{description}
\end{multicols}
